---
params: 
  title: ""
  publication_date: ""
  doi: ""
  github: ""
  lang: ""
output:
  html_document:
    anchor_sections: false
    theme: null
    highlight: null
    mathjax: null
    css: ["style.css", "https://fonts.googleapis.com/css?family=Source+Sans+Pro:400,700&display=swap"]
    self_contained: true
# # To produce Word output, just comment the output lines above and uncomment 
# # the ones here. 
# output: word_document
# always_allow_html: yes
title: "`r params$title`"
---

```{r general-setup, include=FALSE}
## This file contains the FRENCH version of the data story

# Set general chunk options
knitr::opts_chunk$set(
  echo = FALSE, fig.showtext = TRUE, fig.retina = 3,
  fig.align = "center", warning = FALSE, message = FALSE
)

# Install snf.datastory package if not available, otherwise load it
if (!require("snf.datastory")) {
  if (!require("devtools")) {
    install.packages("devtools")
    library(devtools)
  }
  install_github("snsf-data/snf.datastory")
  library(snf.datastory)
}

# Load packages
library(tidyverse)
library(lubridate)
library(scales)
library(conflicted)
library(jsonlite)
library(patchwork)
library(here)
library(glue)
library(ggiraph)

# Conflict preferences
conflict_prefer("filter", "dplyr")
conflict_prefer("get_datastory_theme", "snf.datastory")
conflict_prefer("get_datastory_scheme", "snf.datastory")

# Increase showtext package font resolution
showtext_opts(dpi = 320)

# Set the locale for date formatting (Windows)
Sys.setlocale("LC_TIME", "French")

# Set the language for this rmd for translate function
lang <- "fr"

# Create function to print number with local language-specific format
print_num <- function(x) snf.datastory::print_num(x, lang = lang)

# Knitr hook for local formatting of printed numbers
knitr::knit_hooks$set(
  inline = function(x) {
    if (!is.numeric(x)) {
      x
    } else {
      print_num(x)
    }
  }
)

# Function that returns the desired language version of a string, given three
# language strings are provided to the function 
translate <- function(en_string = "NOT TRANSLATED",
                      de_string = "NOT TRANSLATED",
                      fr_string = "NOT TRANSLATED",
                      lang = "en") {
  string <- case_when(lang == "en" ~ en_string, 
                      lang == "de" ~ de_string, 
                      lang == "fr" ~ fr_string, 
                      TRUE ~ "NO VALID LANGUAGE SPECIFIED")
  string
}
```

```{r print-header-infos, results='asis'}
# Add publication date to header
cat(format(as_datetime(params$publication_date), "%d.%m.%Y"))

# Register the Google font (same as Data Portal, is not loaded twice)
cat(paste0(
  "<link href='https://fonts.googleapis.com/css?family=",
  "Source+Sans+Pro:400,700&display=swap' rel='stylesheet'>"
))
```
```{r story-specific-setup, include=FALSE}
# Load data about funding in 2022
funding_in_2022 <- 
  read_csv(here("data", "prelim_funding_in_2022_20230201.csv"))
# Übergangsmassnahmen Horizon Europe
# Get the amount going to Horizon Transitional Measures
horizon_measures <- funding_in_2022 |> 
  filter(str_detect(FundingInstrumentGaReporting, "Horizon")) |> 
  summarise(sum_amount = sum(AmountGranted)) |> 
  pull()

# Total granted amount
sum(funding_in_2022$AmountGranted)
```


<!-- Short lead (2-3 sentences) in bold -->

**Premiers chiffres provisoires&nbsp;: en 2022, le FNS a investi 912&nbsp;millions de francs dans le cadre de ses instruments d’encouragement réguliers. Nous avons également alloué 173&nbsp;millions aux mesures transitoires Horizon Europe.**

Plus de 500&nbsp;millions de francs ont été consacrés à l’encouragement de projets, dans le cadre desquels des chercheuses et chercheurs expérimentés réalisent leurs propres idées. Nous avons accordé environ 180&nbsp;millions tant pour le travail des groupes de recherche dans les programmes que pour les jeunes chercheuses et chercheurs dans les instruments d’encouragement de carrière. 

La Suisse n’est pas associée à Horizon Europe, le programme-cadre de l’UE pour la recherche et l’innovation. C’est pourquoi le FNS a accordé l’année dernière 173&nbsp;millions de francs pour des projets dans le cadre de mesures transitoires. Le budget de l’instrument d’encouragement Eccellenza, que nous avons intégré dans les mesures transitoires, y est également inclus. Ces mesures profitent aussi bien aux jeunes scientifiques qu’aux chercheuses et chercheurs confirmés. 

En outre, le FNS verse aux hautes écoles plus de 100&nbsp;millions de francs pour l’indemnisation des coûts indirects de la recherche (overhead), qui sont générés en raison des nouveaux projets. 

Fin 2022, 5500&nbsp;projets que nous soutenons étaient en cours, impliquant environ 20'000&nbsp;chercheuses et chercheurs dans les hautes écoles et d’autres institutions. La plupart des projets courent sur plusieurs années. 

Le graphique montre la répartition des subventions accordées entre les différentes catégories. En raison des mesures transitoires d’Horizon Europe, les chiffres ne sont que partiellement comparables avec ceux des années précédentes. 

<div class="hide-mobile hide-tablet" style="width: 800px;position: relative;max-width: 800px;left: -70px;border-top: 1px solid #d3d3d3;border-bottom: 1px solid #d3d3d3;padding-top: 20px;margin: 20px 0;">
<div class="plot-box">
<div class="plot-title">Montants des encouragements FNS approuvés en 2022 (chiffres provisoires)</div>

```{r, out.width="100%", fig.height=2.5}
# Color settings: Colors for the LVL 1 instruments are defined as in the
# Data Portal (YAAY scheme)
get_color_palette_lvl_1 <- function(lang) {
  tibble(
    FundingInstrumentGaLevel1 = c(
      translate("Projects", "Projekte", "Projets", 
                lang),
      translate("Careers", "Karrieren", "Carrières", lang),
      translate("Programmes", "Programme", "Programmes", lang),
      translate("Infrastructure", "Infrastrukturen", "Infrastructures", lang),
      translate("Science communication", "Wissenschaftskommunikation", 
                "Communication scientifique", lang), 
      translate("Horizon Europe Transitional Measures", 
                "Übergangsmassnahmen Horizon Europe", 
                "Mesures transitoires Horizon Europe", lang)
    ),
    # Use slightly adapted SNSF colors for this kind of plot
    color_lvl1 = c("#3D7D9F", "#83D0F5", "#FBBE5E", "#71B294", "#9D90B9",
                            "#3D7D9F")
  )
}

# Function to preprocess the funding data and create summarized data objects
# for the bar plot main bar and the bar that summarizes also the two programmes
# components (general programmes + Horizon transition measures)
preprocess_plot_data <- function(funding_data, lang, 
                                 reverse_order = FALSE) {
  # Mapping table for the translation of the Level 1 Funding Instruments
  mapping_fi <- tibble(
    en = c("Projects", "Careers", "Programmes", 
           "Horizon Europe Transitional Measures", "Infrastructure", 
           "Science communication"),
    de = c("Projekte", "Karrieren", "Programme",
           "Übergangsmassnahmen Horizon Europe", "Infrastrukturen", 
           "Wissenschaftskommunikation"),
    fr = c("Projets", "Carrières", "Programmes",
           "Mesures transitoires Horizon Europe", 
           "Infrastructures", "Communication scientifique")
  ) %>% 
    # Now choose the English string (to join and the destination lang string)
    mutate(FundingInstrumentGaLevel1 = en) %>% 
    select(FundingInstrumentGaLevel1, destination = any_of(lang))
  
  # Compile the text string to be displayed in the tooltip
  tooltip_text <- funding_data %>% 
    mutate(grouping_scheme = if_else(str_detect(FundingInstrumentGaLevel1, "Horizon Europe"), 
                                     FundingInstrumentGa, 
                                     FundingInstrumentGaReporting_Fr)) %>% 
    group_by(FundingInstrumentGaLevel1, grouping_scheme) %>%
    summarise(scheme_granted = sum(AmountGranted, na.rm = TRUE),
              n = n()) %>% 
    ungroup() %>% 
    group_by(FundingInstrumentGaLevel1) %>% 
    arrange(desc(scheme_granted)) %>% 
    summarise(tooltip = paste0("<strong>", grouping_scheme, "</strong> (",
                                translate("CHF ", 
                                         "", 
                                         "", 
                                         lang), 
                               # For smaller amounts, don't round down to zero
                               if_else(scheme_granted < 50000, 
                                       print_num(round(scheme_granted / 1000000, 
                                                       digits = 2)), 
                                       print_num(round(scheme_granted / 1000000, 
                                                       digits = 1))), 
                               
                               translate(" million approved in ", 
                                         " Mio. CHF zugesprochen in ", 
                                         " mio CHF approuvés pour ", 
                                         lang), 
                               print_num(n), 
                               translate(" grants)",
                                         " Beiträgen)",
                                         " contributions)", 
                                         lang)
                               ,
                               collapse = "<br>")) |> 
    ungroup()
  
  # Helper function to reverse the order depending on an argument
  order_data <- function(data, reverse_order = FALSE) {
    if (reverse_order) {
      data %>%
        mutate(order = nrow(.) - row_number())
    } else {
      data %>%
        mutate(order = row_number())
    }
  }
  
  # Prepare plot data, calculate frequencies of granted amounts per LVL 1 FI
  # (Careers, Programmes...)
  plot_data <- funding_data %>% 
    group_by(FundingInstrumentGaLevel1) %>%
    summarise(lvl_1_granted = sum(AmountGranted, na.rm = TRUE),
              n = n()) %>%
    # Get translated version of FundingInstrumentGaLevel1
    left_join(mapping_fi, by = "FundingInstrumentGaLevel1") %>% 
    # Add scheme-level tooltip text data
    left_join(tooltip_text, by = "FundingInstrumentGaLevel1") %>% 
    # Overwrite with the destination language string
    mutate(FundingInstrumentGaLevel1 = destination) %>% 
    mutate(lvl_1_freq = lvl_1_granted / sum(lvl_1_granted)) %>%
    # Order the data for the plot: by LVL 1 share size
    arrange(desc(lvl_1_freq)) %>%
    order_data(reverse_order = reverse_order) %>%
    # Now calculate where the segment has to start (and end) per LVL 1 FI
    mutate(seg_start = map_dbl(order, function(x) {
      prev_dist <- filter(., order < x) %>%
        pull(lvl_1_granted) %>%
        sum(na.rm = TRUE)
      prev_dist
    }),
    seg_end = seg_start + lvl_1_granted)
  
  # Return the two data objects as list
  return(plot_data)
}

# Function to draw the bar chart for desktops
draw_funding_portfolio_5 <- function(lang = "en") {
  ## Prepare the data for the plot
  # Without Horizon
  preproc_data <-
    preprocess_plot_data(
      funding_data = funding_in_2022 |> 
        filter(!str_detect(FundingInstrumentGaReporting, "Horizon")), lang, 
      reverse_order = FALSE) |>  
    mutate(
      type = 
        translate(
          "Regular SNSF funding instruments (CHF 912 million)",
          "Reguläre Förderinstrumente (912 Mio. CHF)",
          "Instruments d’encouragement réguliers du FNS (912  mio CHF)", 
          lang)
    ) |> 
    # Add only Horizon
    bind_rows(
      preprocess_plot_data(
        funding_data = funding_in_2022 |> 
          filter(str_detect(FundingInstrumentGaReporting, "Horizon")), lang, 
        reverse_order = FALSE) |>  
        mutate(
          type = 
            translate(
              "Horizon Europe transitional measures*",
              "Übergangsmassnahmen Horizon Europe*",
              "Mesures transitoires Horizon Europe*", 
              lang)
        )
    )
  
  # Get manual color palette based on lang-specific values
  color_palette_lvl1 <- get_color_palette_lvl_1(lang)
  
  # Create the plot
  p_funding_portfolio_5 <- preproc_data %>%
    filter(!str_detect(FundingInstrumentGaLevel1, "Horizon")) %>%
    ggplot(aes(x = 1, y = lvl_1_granted,
               fill = reorder(FundingInstrumentGaLevel1, -order), 
               tooltip = tooltip)) +
    geom_col_interactive(color = "white", width = 0.7) +
    # Level 1 FI labels
    # Bold text (FI and percentage)
    geom_text(
      aes(
        x = if_else(lvl_1_granted < 30 * 10^6, 1.6, 2), 
        y = seg_start,
        label = FundingInstrumentGaLevel1, 
        angle = if_else(lvl_1_granted < 30 * 10^6, 90, 0),
        hjust = 0),
      vjust = 1,
      color = "#4d4d4d", family = "Source Sans Pro",
      size = 2.75, fontface = "bold") +
    # Plain text (amount)
    geom_text(
      aes(x = if_else(lvl_1_granted < 30 * 10^6, 1.375, 1.7),
          y = if_else(lvl_1_granted < 30 * 10^6, seg_start + 0.018, seg_start),
          label = 
            if_else(
              # Don't show amount for <30 mio, not enough space
              lvl_1_granted < 30 * 10^6, 
              "", 
              paste0(translate("CHF ", 
                                  "", 
                                  "", 
                                  lang),
                        round((lvl_1_granted / 1000000)),
                        translate(" million", 
                                  " Mio. CHF", 
                                  " mio CHF", 
                                  lang)
              )
            ),
          angle = if_else(lvl_1_granted < 30 * 10^6, 90, 0)),
      vjust = 1,
      hjust = 0,
      color = "#4d4d4d", family = "Source Sans Pro",
      size = 2.5, fontface = "plain") +
    coord_flip() +
    get_datastory_theme(remove_plot_margin = TRUE) + 
    scale_fill_manual(
      values = setNames(color_palette_lvl1$color_lvl1, 
                        color_palette_lvl1$FundingInstrumentGaLevel1), 
      guide = "none") +
    scale_color_manual(
      guide = "none",
      values = get_datastory_scheme()
    ) +
    labs(x = NULL, y = NULL) +
    theme(
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      panel.grid.major.x = element_blank(),
    ) +
    expand_limits(x = 3.5) +
    facet_wrap(~type, ncol = 1) + 
    theme(strip.text = element_text(hjust = 0))
  
  p_funding_portfolio_5
  
}

# Create ggiraph object
girafe(ggobj = draw_funding_portfolio_5(lang), 
       height_svg = 2.5, 
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F08262;stroke:#F08262;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))
```

```{r, out.width="100%", fig.height=1.5}

# Function to draw the bar chart for desktops
draw_funding_portfolio_5_horizon <- function(lang = "en") {
  ## Prepare the data for the plot
  # Without Horizon
  preproc_data <-
    preprocess_plot_data(
      funding_data = funding_in_2022 |> 
        filter(!str_detect(FundingInstrumentGaReporting, "Horizon")), lang, 
      reverse_order = FALSE) |>  
    mutate(
      type = 
        translate(
          "Regular SNSF funding instruments (CHF 912 million)",
          "Reguläre Förderinstrumente (912 Mio. CHF)",
          "Instruments d’encouragement réguliers du FNS (912  mio CHF)",
          lang)
    ) |> 
    # Add only Horizon
    bind_rows(
      preprocess_plot_data(
        funding_data = funding_in_2022 |> 
          filter(str_detect(FundingInstrumentGaReporting, "Horizon")), lang, 
        reverse_order = FALSE) |>  
        mutate(
          type = 
            translate(
              "Horizon Europe transitional measures*",
              "Übergangsmassnahmen Horizon Europe*",
              "Mesures transitoires Horizon Europe*",
              lang)
        )
    )
  
  # Get manual color palette based on lang-specific values
  color_palette_lvl1 <- get_color_palette_lvl_1(lang)
  
  
  p_funding_portfolio_5_horizon <-
    preproc_data %>%
    filter(str_detect(FundingInstrumentGaLevel1, "Horizon")) %>%
    ggplot(aes(x = 0, y = lvl_1_granted,
               fill = reorder(FundingInstrumentGaLevel1, -order), 
               tooltip = tooltip)) +
    geom_col_interactive(color = "white", width = 0.87) +
    geom_text(
      aes(x = 0.9,
          y = if_else(lvl_1_granted < 30 * 10^6, seg_start + 0.018, seg_start),
          label = 
            paste0(translate("CHF ", 
                             "", 
                             "", 
                             lang),
                   round((lvl_1_granted / 1000000)),
                   translate(" million", 
                             " Mio. CHF", 
                             " mio CHF", 
                             lang)
            )
      ),
      vjust = 1,
      hjust = 0,
      color = "#4d4d4d", family = "Source Sans Pro",
      size = 2.5, fontface = "plain") +
    coord_flip() +
    get_datastory_theme(remove_plot_margin = TRUE) + 
    scale_fill_manual(
      values = setNames(color_palette_lvl1$color_lvl1, 
                        color_palette_lvl1$FundingInstrumentGaLevel1), 
      guide = "none") +
    scale_color_manual(
      guide = "none",
      values = get_datastory_scheme()
    ) +
    labs(
      x = NULL,
      y = NULL,
      caption =
        translate(
          "*Financed with additional funds from the federal government and funds from the career funding budget (Eccellenza scheme).",
          "*Finanziert durch zusätzliche Mittel des Bundes und durch Mittel aus dem Budget der Karriereförderung (Instrument Eccellenza).", 
          "*Financé par des fonds supplémentaires de la Confédération et par des fonds du budget d’encouragement de carrière (instrument Eccellenza).", 
          lang)
    ) +
    theme(
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      panel.grid.major.x = element_blank(),
    ) +
    expand_limits(y = sum(preproc_data$lvl_1_granted[1:5]), x = 1.3) +
    facet_wrap(~type, ncol = 1) +
    theme(
      strip.text = element_text(hjust = 0),
      plot.caption = element_text(hjust = 0.04, face = "plain")
    )
  
  p_funding_portfolio_5_horizon
  
}

# Create ggiraph object
girafe(ggobj = draw_funding_portfolio_5_horizon(lang), 
       height_svg = 1.5, 
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F08262;stroke:#F08262;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))
```
<div class="caption">
Données&nbsp;: subsides FNS accordés en 2022 (chiffres provisoires, état au 1&nbsp;février 2023&nbsp;; sans indemnisation des coûts indirects de la recherche des hautes écoles et sans les subsides pour les articles de revues en Open Access).
</div>
</div>
</div>

<div class="hide-desktop">
<div class="plot-box">
<div class="plot-title">Montants des encouragements FNS approuvés en 2022 (chiffres provisoires)</div>
```{r, out.width="100%", fig.width=3, fig.height=10}
# Function to draw the bar chart for mobile devices
draw_funding_portfolio_5_mob <- function(lang = "en") {
  ## Prepare the data for the plot
  # Without Horizon
  preproc_data <-
    preprocess_plot_data(
      funding_data = funding_in_2022 |> 
        filter(!str_detect(FundingInstrumentGaReporting, "Horizon")), lang, 
      reverse_order = TRUE) |>  
    mutate(
      type =
        translate(
          "Regular SNSF funding instruments (CHF 912 million)",
          "Reguläre Förderinstrumente (912 Mio. CHF)",
          "Instruments d’encouragement réguliers du FNS (912  mio CHF)",
          lang
        )
    ) |> 
    # Add only Horizon
    bind_rows(
      preprocess_plot_data(
        funding_data = funding_in_2022 |> 
          filter(str_detect(FundingInstrumentGaReporting, "Horizon")), lang, 
        reverse_order = TRUE) |>  
        mutate(
          type = 
            translate(
              "Horizon Europe transitional measures*",
              "Übergangsmassnahmen Horizon Europe*",
              "Mesures transitoires Horizon Europe*",
              lang)
        )
    )
  
  # Get manual color palette based on lang-specific values
  color_palette_lvl1 <- get_color_palette_lvl_1(lang)
  
  # Create the plot
  p_funding_portfolio_5 <-
    preproc_data %>%
    filter(!str_detect(FundingInstrumentGaLevel1, "Horizon")) %>%
    ggplot(aes(x = 1, y = lvl_1_granted,
               fill = reorder(FundingInstrumentGaLevel1, -order), 
               tooltip = tooltip)) +
    geom_col_interactive(color = "white", width = 0.7) +
    # Level 1 FI labels
    # Bold text (FI and percentage)
    geom_text(aes(x = 1.5,
                  y = seg_end,
                  label = if_else(
                    str_detect(FundingInstrumentGaLevel1, "Horizon"), 
                    str_wrap(FundingInstrumentGaLevel1, 25), 
                    FundingInstrumentGaLevel1
                  ), 
                  hjust = 0),
              vjust = 1,
              lineheight = 0.75, 
              color = "#4d4d4d", family = "Source Sans Pro",
              size = 3, fontface = "bold") +
    # Plain text (amount)
    geom_text(aes(x = 1.5,
                  y = if_else(str_detect(FundingInstrumentGaLevel1, "Horizon"), 
                              seg_end - 70 * 10^6, 
                              seg_end - 35 * 10^6),
                  label = 
                    if_else(
                      # Don't show amount for <30 mio, not enough space
                      lvl_1_granted < 30 * 10^6, 
                      "", 
                      paste0(
                        translate("CHF ", 
                                  "", 
                                  "", 
                                  lang),
                        round((lvl_1_granted / 1000000)),
                        translate(" million", 
                                  " Mio. CHF", 
                                  " mio CHF", 
                                  lang)
                      )
                    )), 
              vjust = 1,
              hjust = 0,
              color = "#4d4d4d", family = "Source Sans Pro",
              size = 3, fontface = "plain") +
    get_datastory_theme() + 
    scale_fill_manual(
      values = setNames(color_palette_lvl1$color_lvl1,
                        color_palette_lvl1$FundingInstrumentGaLevel1),
      guide = "none") +
    scale_y_continuous(labels = function(x) { paste0(x / 10^6) },
                       breaks = seq(0, 10^9, 2 *10^8)) +
    scale_color_manual(
      guide = "none",
      values = setNames(color_palette_lvl1$color_lvl1,
                        color_palette_lvl1$FundingInstrumentGaLevel1)
    ) +
    labs(x = NULL, y = NULL) +
    theme(axis.text.x = element_blank(),
          panel.grid.major.y = element_blank()) +
    expand_limits(x = 4) + 
    facet_wrap(~type, ncol = 1) + 
    theme(strip.text = element_text(hjust = 0), 
          axis.text.y = element_blank(),
          axis.ticks.y = element_line(color = "#d3d3d3", linewidth = 0.3))
  
  p_funding_portfolio_5_horizon <-
    preproc_data %>%
    filter(str_detect(FundingInstrumentGaLevel1, "Horizon")) %>%
    ggplot(aes(x = 1, y = lvl_1_granted,
               fill = reorder(FundingInstrumentGaLevel1, -order), 
               tooltip = tooltip)) +
    geom_col_interactive(color = "white", width = 0.7) +
    # Level 1 FI labels
    # Bold text (FI and percentage)
    geom_text(aes(x = 1.5,
                  y = seg_end,
                  label = if_else(
                    str_detect(FundingInstrumentGaLevel1, "Horizon"), 
                    str_wrap(FundingInstrumentGaLevel1, 25), 
                    FundingInstrumentGaLevel1
                  ), 
                  hjust = 0),
              vjust = 1,
              lineheight = 0.75, 
              color = "#4d4d4d", family = "Source Sans Pro",
              size = 3, fontface = "bold") +
    # Plain text (amount)
    geom_text(aes(x = 1.5,
                  y = if_else(str_detect(FundingInstrumentGaLevel1, "Horizon"), 
                              seg_end - 70 * 10^6, 
                              seg_end - 35 * 10^6),
                  label = 
                    if_else(
                      # Don't show amount for <30 mio, not enough space
                      lvl_1_granted < 30 * 10^6, 
                      "", 
                      paste0(translate("CHF ", 
                                  "", 
                                  "", 
                                  lang),
                        round((lvl_1_granted / 1000000)),
                        translate(" million", 
                                  " Mio. CHF", 
                                  " mio CHF", 
                                  lang)
                      )
                    )), 
              vjust = 1,
              hjust = 0,
              color = "#4d4d4d", family = "Source Sans Pro",
              size = 3, fontface = "plain") +
    get_datastory_theme() + 
    scale_fill_manual(
      values = setNames(color_palette_lvl1$color_lvl1,
                        color_palette_lvl1$FundingInstrumentGaLevel1),
      guide = "none") +
    scale_y_continuous(labels = function(x) { paste0(x / 10^6) },
                       breaks = seq(0, 10^9, 2 *10^8)) +
    scale_color_manual(
      guide = "none",
      values = setNames(color_palette_lvl1$color_lvl1,
                        color_palette_lvl1$FundingInstrumentGaLevel1)
    ) +
    labs(
      x = NULL,
      y = NULL,
      caption =
        translate(
          str_wrap(
            c(
              "*Financed with additional funds from the federal government and funds from the career funding budget (Eccellenza scheme).",
              "*Finanziert durch zusätzliche Mittel des Bundes und durch Mittel aus dem Budget der Karriereförderung (Instrument Eccellenza).", 
              "*Financé par des fonds supplémentaires de la Confédération et par des fonds du budget d’encouragement de carrière (instrument Eccellenza)."
            ),
            width = 80
          ), 
          lang)
    ) +
    theme(axis.text.x = element_blank(),
          panel.grid.major.y = element_blank()) +
    expand_limits(x = 4) + 
    facet_wrap(~type, ncol = 1) + 
    theme(strip.text = element_text(hjust = 0), 
          axis.text.y = element_blank(),
          axis.ticks.y = element_line(color = "#d3d3d3", linewidth = 0.3),
          plot.caption = element_text(hjust = 0, face = "plain"))
  
  p_funding_portfolio_5  + p_funding_portfolio_5_horizon +
    plot_layout(ncol = 1, heights = c(0.5, 0.173))
}

# Create ggiraph object
girafe(ggobj = draw_funding_portfolio_5_mob(lang),
       width_svg = 3,
       height_svg = 10,
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F08262;stroke:#F08262;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))
```
<div class="caption">
Données&nbsp;: subsides FNS accordés en 2022 (chiffres provisoires, état au 1&nbsp;février 2023&nbsp;; sans indemnisation des coûts indirects de la recherche des hautes écoles et sans les subsides pour les articles de revues en Open Access).
</div>
</div>
</div>

Les données, le texte et le code de ce récit de données sont <a href="`r params$github`" target="_blank">disponibles sur Github</a> et <a href="`r params$doi`" target="_blank">archivés sur Zenodo</a>.<br>DOI: `r str_remove(params$doi, "https://doi.org/")`

```{r prevent-internal-snsf-packages, include=FALSE}
# Internal SNSF packages must not be used in data stories, as their
# pre-processing functions are internal and the corporate design differs from
# the data portal.
if (any(c("snfverse", "snf.preprocessing", "snf.plot") %in% 
        loadedNamespaces())) {
  stop(glue(
    "You must not use internal SNSF packages in data stories.",
    " Please resort to snf.datastory."
  ))
}
```
